Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-09 draft/accordionComplexSurfaces.tex
Added a geometric proof.

\para{Geometric proof}
\vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}

>>>>

\para{Geometric proof}
The statement of the lemma translates on~$\surface(\bar Q)$ as follows: for any facet~$F$ of the non-crossing complex~$\NCC$ and any puncture of the dissection~$\dissection_{\bar Q}$, there exists a curve in~$F$ which goes to the puncture.
Assume that there is a puncture with no curves of~$F$ going to it.
Construct a curve~$\gamma$ as follows:~$\gamma$ first unwinds from the puncture, then~$\gamma$ leaves the local picture around the puncture by turning aroune another marked point (marked~$X$ on the picture below).

\pierreguy{Pic No 7 here.}
Two situations occur.

Firstly, if there are no curves of~$F$ closer to~$X$ than~$\gamma$, then~$\gamma$ can circle around~$X$ until it reaches the boundary (if~$X$ is on the boundary) or infinitely (if~$X$ is a puncture).
Then~$\gamma$ is a~$\dissection_{\bar Q}$-accordion which crosses none of those in~$F$, contradicting the maximality of~$F$.

Secondly, if there is a curve of~$F$ closer to~$X$ than~$\gamma$, then let~$\delta$ be the one furthest from~$X$ ($\delta$ exists by Lemma \ref{lemm:facesHaveMaximalElement}).
From there, let~$\gamma$ follow~$\delta$ on the surface until it either reaches the boundary or circles infinitely around a puncture.  
Then~$\gamma$ is compatible with all curves in~$F$, a contradiction.

Thus~$F$ contains a curve going to the puncture.
\vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}
\pierreguy{Done; I will need two pictures, please, Vincent.}
